---
title: "Prepare Climate Data"
---

[日本語版はこちら (Japanese version)](prepare_climate_data_ja.qmd)

This chapter creates climate variables from Average Value Mesh Data.
The data source is NLNI's [Average Value Mesh Data](https://nlftp.mlit.go.jp/ksj/gml/datalist/KsjTmplt-G02-v3_0.html).

## Download Average Value Mesh Data

Download required data from:

- [Average Value Mesh Data](https://nlftp.mlit.go.jp/ksj/gml/datalist/KsjTmplt-G02-v3_0.html)

Data files are distributed as ZIP files. Extract them after download.

Store downloaded data in any folder. In this project, the path is set through the `PROJECT_DATA_DIR` environment variable.

```{.bash filename=".Renviron"}
PROJECT_DATA_DIR=C:/Users/Username/Dropbox/GitHub/japanese_climate_calculation
```

::: {.callout-note}
## Terms of use

Please check the NLNI terms of use [here](https://nlftp.mlit.go.jp/ksj/other/agreement.html).
:::

## Load libraries

```{r}
library(tools)
library(sf)
```

## Set the data directory

```{r}
data_dir <- Sys.getenv("PROJECT_DATA_DIR")
# If the environment variable is not set:
# data_dir <- "data"
```

## Extract ZIP files

```{r}
zip_output_dir <- file.path("data", "climate_mesh_data")
dir.create(zip_output_dir, showWarnings = FALSE, recursive = TRUE)

zip_files <- list.files(
  file.path(data_dir, "climate_mesh_data_zip"),
  pattern = "^G02-22_.*\\.zip$",
  full.names = TRUE
)
file_names <- tools::file_path_sans_ext(basename(zip_files))
lapply(zip_files, unzip, overwrite = TRUE, exdir = zip_output_dir)
```

## Read shapefiles

```{r}
data_list <- list()
data_paths <- list.files(
  zip_output_dir,
  pattern = "^G02-22_.*\\.shp$",
  full.names = TRUE,
  recursive = TRUE
)

for (i in seq_along(data_paths)) {
  path <- data_paths[i]
  name <- file_path_sans_ext(basename(path))
  data_list[[name]] <- st_read(path)
}
sf_climate <- do.call(rbind, data_list)

df_label <- read.csv(
  file.path(data_dir, "manual/mesh_climate_data_labels.csv"),
  fileEncoding = "UTF-8"
)
names(sf_climate) <- make.names(c(df_label$name_en, "geometry"))
```

## Convert values

Values are scaled by 10 in the source data; divide by 10 to recover original units.
Missing values are encoded as `999999`.

```{r}
col_index <- c(
  grep("precipitation", names(sf_climate)),
  grep("temperature", names(sf_climate)),
  grep("sunshine_duration", names(sf_climate)),
  grep("global_solar_radiation", names(sf_climate))
)
indices_snow <- grep("maximum_snow_depth", names(sf_climate))

NA_value <- 999999
df <- st_drop_geometry(sf_climate)
df[, col_index][df[, col_index] == NA_value] <- NA
df[, col_index] <- df[, col_index] * 0.1
df[, indices_snow][df[, indices_snow] == NA_value] <- 0
sf_climate <- st_set_geometry(df, st_geometry(sf_climate))
```

## Extract longitude and latitude

```{r}
sf_climate$longitude <- st_coordinates(st_centroid(sf_climate))[, 1]
sf_climate$latitude <- st_coordinates(st_centroid(sf_climate))[, 2]
```

## Save data

```{r}
save_dir <- file.path(data_dir, "climate_mesh_data_joined")
dir.create(save_dir, showWarnings = FALSE, recursive = TRUE)
saveRDS(sf_climate, file.path(save_dir, "climate_mesh_data.rds"))
```

## Save as CSV

```{r}
df_climate <- st_drop_geometry(sf_climate)
write.csv(
  df_climate,
  file.path(save_dir, "climate_mesh_data.csv"),
  row.names = FALSE,
  fileEncoding = "UTF-8"
)
```
